---
title: "Diamond Drill with dplyr"
author: "Li-Ta Lo"
date: "February 11, 2016"
output: 
  ioslides_presentation: 
    highlight: tango
---

```{r echo = FALSE}
library(dplyr)
data(diamonds, package = "ggplot2")
```

## Problem 1. {.build}

Make a new data set that has the average depth and price of the diamonds in the data set

```{r}
diamonds %>% summarise(avg_depth = mean(depth),
                       avg_price = mean(price))
```

## Problem 2. {.build}

Add a new column to the data set that records each diamond's price per carat.

```{r}
diamonds %>% mutate(price_per_carat = price/carat)
```

## Problem 3. {.build}

Make a data set that only includes diamonds with an Ideal cut.

```{r}
diamonds %>% filter(cut == "Ideal")
```

## Problem 4. {.build}

Create a new data set that groups diamonds by their cut and displays the average
price of each group.

```{r}
diamonds %>%
    group_by(cut) %>%
    summarise(avg_price = mean(price))
```

## Problem 5 {.build}

Create a new data set that groups diamonds by color and displays the average
depth and average table for each group.

```{r}
diamonds %>%
    group_by(color) %>%
    summarise(avg_depth = mean(depth),
              avg_table = mean(table))
```

## Problem 6. {.build}

Add two columns to the diamonds data set. The first column should display the
average depth of diamonds in the diamond's color group. The second column should
display the average table of diamonds in the diamonds color group.

```{r}
diamonds %>%
    group_by(color) %>%
    mutate(avg_depth = mean(depth),
           avg_table = mean(table))
```

## Problem 7. {.build}

Make a data set that contains all of the unique combinations of cut, color, and
clarity, as well the average price of diamonds in each group.

```{r}
diamonds %>%
    group_by(cut, color, clarity) %>%
    summarise(avg_price = mean(price))
```

## Problem 8. {.build}

Add a column to the diamonds data set that displays the average price for all
diamonds with a diamond's cut, color, and clarity. 

```{r}
diamonds %>%
    group_by(cut, color, clarity) %>%
    mutate(avg_price = mean(price))
```

## Problem 9. {.build}

Do diamonds with the best cut fetch the best price for a given amount of carats?

```{r}
diamonds %>%
    group_by(cut) %>%
    summarise(avg_price = mean(price/carat))
```

## Problem 10. {.build}

Which color diamonds seem to be largest on average (in terms of carats)?

```{r}
diamonds %>%
    group_by(color) %>%
    summarise(avg_carat = mean(carat))
```

## Problem 11. {.build}

What color of diamonds occurs the most frequently among diamonds with ideal cuts?

```{r}
diamonds %>%
    group_by(color) %>%
    summarise(count = n())
```

## Problem 12. {.build}

Which clarity of diamonds has the largest average table per carats?

```{r}
diamonds %>%
    group_by(clarity) %>%
    summarise(avg_table_per_carat = mean(table/carat)) %>%
    arrange(avg_table_per_carat)
```

## Problem 13. {.build}

Which diamond has the largest price per carat compared other diamonds with its
cut, color, and clarity?

```{r}
diamonds %>%
    group_by(cut, color, clarity) %>%
    mutate(diff = price - mean(price)) %>%
    ungroup() %>%
    top_n(1, diff)
```

## Problem 14. {.build}

What is the average price per carat of diamonds that cost more than $10000?

```{r}
diamonds %>% filter(price > 10000) %>% summarise(mean(price/carat))
```

## Problem 15. {.build}

Display the largest diamond depth observed for each clarity group.

```{r}
diamonds %>% group_by(clarity) %>% summarise(max(depth))
```
